Group assignment

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

```{r echo=FALSE}
kable(corr_table1)
```

@@

# Graph to show the correlation pattern by each country:
```{r echo=FALSE}
ggplot(corr_table1, aes(x = correlation ,
                       y = fct_reorder(country, correlation))) +
  geom_point(color = 'red', size = 2)+
  labs(y='Countries',x='Correlation')
```

>>>>

```{r echo=FALSE}
kable(corr_table1)
```
# Graph to show the correlation pattern by each country:
```{r echo=FALSE}
ggplot(corr_table1, aes(x = correlation ,
                       y = fct_reorder(country, correlation))) +
  geom_point(color = 'red', size = 2)+
  labs(y='Countries',x='Correlation')
```

@@
